Multi sky-view\\ 3D aerosol distribution recovery

### 2013-08-04 article.tex
Added OCIS codes.
Yoav fixes with small updates by me.

\ocis{(000.0000)
  General.} % REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE

@@

@@

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is
distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{Boas2001,messer}. In
contrast, our source is the uncontrolled, unidirectional
Sun. Moreover, typical tomography relies on a linear
model~\cite{gregson}: the pixel value is a linear combination of
components along a line of sight (LOS), or a multiplicative
combination (linearized by a logarithm). Linear tomography can detect
gases~\cite{Cosofret2009}, which absorb UV or IR radiation. However,
aerosol attenuation of visible light is typically dominated by {\em
  scattering}, rather than absorption. Since the radiation source is
single and fixed in space and time, we cannot rely on direct
illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}

@@

\section{Theoretical Background}
\label{sec:theor-backgr}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} for interacting with the irradiance. For
an aerosol the cross section is denoted $\sigma^{\rm aerosol}$.  The
aerosol density is $n$. Per unit volume, the {\em extinction
  coefficient} due to aerosols is $\beta^{\rm aerosol}= \sigma^{\rm
  aerosol} n$. In addition, the atmosphere contains air molecules.
The extinction coefficient due to the molecules is $\beta^{\rm air}$.
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential optical depth,
$d\tau= (\beta^{\rm aerosol}+\beta^{\rm air}) dl$.  The {\em optical
  depth} aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int (\beta^{\rm aerosol}+\beta^{\rm air}) dl =\int
  (\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm air}+ \int
  \sigma^{\rm aerosol} n dl \;,
  \label{eq:tau}
\end{align}
where $\tau^{\rm air}=\int \beta^{\rm air} dl$.  Through an
attenuating atmosphere, the {\em transmittance} exponentially decays
with the optical depth:
\begin{align}
  t=\exp(-\tau) \;.
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} of the particle. For an
aerosol, the single scattering albedo is denoted $\varpi^{\rm
  aerosol}$.  The {\em scattering coefficient} due to aerosols in the
volume is
\begin{align}
  \alpha^{\rm aerosol}= \varpi^{\rm aerosol}\beta^{\rm aerosol}
  =\varpi^{\rm aerosol} \sigma^{\rm aerosol} n \;.
  \label{eq:alph}
\end{align}
The angular distribution of scattering by an aerosol is determined by
a {\em phase function} $P^{\rm aerosol}$, which is normalized: its
integral over all solid angles is unit. Part of the light scatters
towards a camera's LOS, as illustrated in \cref{fig:groundgrid}. The
angle between the SR and LOS is the scattering angle $\Phi^{\rm
  scatter}$. The {\em angular scattering coefficient} due to aerosols
is
\begin{align}
  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter}) = \alpha^{\rm
    aerosol} P^{\rm aerosol}(\Phi^{\rm scatter}) = \varpi^{\rm
    aerosol} \sigma^{\rm aerosol} n P^{\rm aerosol}(\Phi^{\rm
    scatter}).
  \label{eq:alphabasic}
\end{align}
The phase function is often approximated by a parametric expression,
as the Henyey-Greenstein~\cite{Cornette1995} function,
\begin{align}
  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
  g^2)(1+\mu^2) (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}
  \label{eq:aerosol_scatter}
\end{align}
where $g$ is an {\em anisotropy parameter} and $\mu\equiv \cos
\Phi^{\rm scatter}$.

Scattering by air molecules follows the {\em Rayleigh} model. The
phase function is
\begin{align}
  P^{\rm air}\left[\mu\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and the single scattering albedo in visible light is $\varpi^{\rm
  air}$=1. Air molecular density falls off approximately exponentially
with altitude $h$, with a characteristic~\cite{Levi1980} falloff
height $H^\mathrm{air}=8\ \si{\km}$. Thus~\cite{Levi1980}, the
coefficients for extinction and scattering by air molecules can be
modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4} \exp(-h/H^\mathrm{air})
  \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}
where $\lambda$ is the wavelength, in microns.
\\

\noindent {\bf Inverse Transform Sampling}: A tool for RT is
Monte-Carlo (MC) simulation. MC considers scattering and extinction as
random phenomena, that are sampled from their probability
distributions.  Sample random numbers that comply with any known
probability density function can be generated using inverse transform
sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$.

@@

A set of ground-based wide-angle cameras looks upwards
(\cref{fig:groundgrid}), performing {\em integral
  imaging}~\cite{Hong2004} of the sky. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes a first step of formulating a
principle for estimating the 3D atmospheric aerosols distribution,
using such data. To study the feasibility and cross validate it, we
perform RT using two different forward models. A forward model takes
as input a 3D aerosol distribution, and outputs images as if captured
at various viewpoints.  One model uses MC
(\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally
expresses multiple-scattering. Hence, MC rigorously simulates
realistic scenes of arbitrary complexity.
% MC simulations can be made arbitrarily accurate by increasing the
% number of launched %photons. MC methods are highly parallelizable.
The second model uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves RT in an analytic, closed form. This form enables simple
inversion of the model, to estimate the underlying aerosol
distribution (\cref{sec:inverse-problem}).

@@

\section{Single-Scattering Forward Model}
\label{sec:single-scatt-model}

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$, $m$ or $q$. \cref{fig:distributions}.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small [a] and [b] Simulated 3D aerosol distribution
    composed of a {\em Haze Front} and {\em Haze Front}
    respectively. The density units are $10^{6}~{\rm particles}/{\rm
      m}^3.$}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense: inside fog and clouds this model does not
apply. In this model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

\subsection{Optical Depth}
\label{sec:optical-depth}

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$ (See
\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection
line segment has geometric length $l_{\rm SR}(q)$, which depends on
$\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a $N_{\rm voxels}\times
N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$,
whose element $(k,q)$ represents $l_{\rm SR}(q)$:
\begin{equation}
  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  \hspace{-0.05cm}
\end{equation}
The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$ (see
\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
Suppose this LOS intersects voxel $q$. The geometric length of this
intersection line segment is $l_{\rm LOS_c}(m)$ which depends on
$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $m$.  Analogously to
\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
sparse matrix whose element $(k,m)$ is
\begin{equation}
  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,m) =
  \left\{
    \begin{array}{ll}
      l_{{\rm LOS}_c}(m) & \mbox{ if $m \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}

Any voxel generally contains both air molecules and aerosols.  We
focus on situations where there is only a single type of aerosol over
a scene. Hence, the three-element vector $[{\sigma}^{\rm
  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
the density distribution ${\DistUnknown}$ is variable. As a numerical
approximation, assume that within any voxel, the molecular parameters
$\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density
$n(k)$ are constants, e.g., corresponding to the value at each voxel
center.  Following \cref{eq:tau}, the optical depth between the TOA
and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
respectively. Similarly, the optical depth along a LOS to voxel $k$ is
expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
can form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:tau}, the total optical depths corresponding to
LOSs (of camera $c$) and SRs that cross all voxels comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;.
  \label{eq:tautotal}
\end{equation}

@@

\subsection{Image Capture}
\label{sec:captured-image}

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:tautotal}) the radiant power contributed by
the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being
oblivious to all the rest.  Overall, light power captured at a pixel
is a weighted sum of the power $p_c(k)$ from all voxels.  This sum is
formulated by a matrix operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
  pix}$ long.  Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured
image is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
  {\bm D}_c{\bm n})] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

\section{Simulations}
\label{sec:simul}

>>>>

\ocis{
(100.3190)   Inverse problems;
(100.3200)   Inverse scattering;
(280.1100)   Aerosol detection;
(280.1310)   Atmospheric scattering;
(280.4991)   Passive remote sensing.
}

@@

\bibitem{Iwabuchi2006}
H.~Iwabuchi, \enquote{{Efficient Monte Carlo Methods for Radiative Transfer
  Modeling},} Journal of the Atmospheric Sciences \textbf{63}, 2324--2339
  (2006).

@@

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is
distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{Boas2001,messer}. In
contrast, our source is the uncontrolled, unidirectional
Sun. Moreover, typical tomography relies on a linear
model~\cite{gregson}: the pixel value is a linear combination of
components along a line of sight (LOS), or a multiplicative
combination (linearized by a logarithm). Linear tomography can detect
gases~\cite{Cosofret2009}, which absorb UV or IR radiation. However,
aerosol attenuation of visible light is typically dominated by {\em
  scattering}, rather than absorption. Since the radiation source is
single and fixed in space and time, we cannot rely on direct
illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Integral (lightfield) imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}

@@

\section{Theoretical background}
\label{sec:theor-backgr}

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} for interacting with the irradiance. An
aerosol extinction cross section is denoted $\sigma^{\rm aerosol}$.
The aerosol density is $n$. Per unit volume, the {\em extinction
  coefficient} due to aerosols is $\beta^{\rm aerosol}= \sigma^{\rm
  aerosol} n$. In addition, the atmosphere contains air molecules.
The extinction coefficient due to the molecules is $\beta^{\rm air}$.
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential optical depth,
$d\tau= (\beta^{\rm aerosol}+\beta^{\rm air}) dl$.  The {\em optical
  depth} aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int (\beta^{\rm aerosol}+\beta^{\rm air}) dl =\int
  (\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm air}+ \int
  \sigma^{\rm aerosol} n dl \;,
  \label{eq:tau}
\end{align}
where $\tau^{\rm air}=\int \beta^{\rm air} dl$.  Through an
attenuating atmosphere, the {\em transmittance} exponentially decays
with the optical depth:
\begin{align}
  t=\exp(-\tau) \;.
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} of the particle. For an
aerosol, the single scattering albedo is denoted $\varpi^{\rm
  aerosol}$.  The {\em scattering coefficient} due to aerosols in the
volume is
\begin{align}
  \alpha^{\rm aerosol}= \varpi^{\rm aerosol}\beta^{\rm aerosol}
  =\varpi^{\rm aerosol} \sigma^{\rm aerosol} n \;.
  \label{eq:alph}
\end{align}
The angular distribution of scattering by an aerosol is determined by
a {\em phase function} $P^{\rm aerosol}$, which is normalized: its
integral over all solid angles is unit. Part of the light scatters
towards a camera's LOS, as illustrated in \cref{fig:groundgrid}. The
angle between the SR and LOS is the scattering angle $\Phi^{\rm
  scatter}$. The {\em angular scattering coefficient} due to aerosols
is
\begin{align}
  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter}) = \alpha^{\rm
    aerosol} P^{\rm aerosol}(\Phi^{\rm scatter}) = \varpi^{\rm
    aerosol} \sigma^{\rm aerosol} n P^{\rm aerosol}(\Phi^{\rm
    scatter}).
  \label{eq:alphabasic}
\end{align}
% Let $\mu\equiv \cos\Phi^{\rm scatter}$.
The phase function is often approximated by a parametric
expression. Specifically, the Henyey-Greenstein~\cite{Cornette1995}
function is governed by an {\em anisotropy parameter} $g$:
\begin{align}
  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
  g^2)(1+\cos^2\Phi^{\rm scatter}) (2+g^2)^{-1}(1 + g^2 -
  2g\cos\Phi^{\rm scatter})^{-1.5}.
  \label{eq:aerosol_scatter}
\end{align}
% \begin{align}
%   P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \sfrac{3}{8\pi} (1 -
%   g^2)(1+\mu^2) (2+g^2)^{-1}(1 + g^2 - 2g\mu)^{\sfrac{-3}{2}}.
%   \label{eq:aerosol_scatter}
% \end{align}

Scattering by air molecules follows the {\em Rayleigh} model. The
phase function is
\begin{align}
  P^{\rm air}(\Phi^{\rm scatter}) &\approx
  \sfrac{3}{16\pi}(1+\cos^2\Phi^{\rm scatter})
  \label{eq:rayleighP}
\end{align}
and the single scattering albedo in visible light is $\varpi^{\rm
  air}$=1. Air molecular density falls off approximately exponentially
with altitude $h$, with a characteristic~\cite{Levi1980} falloff
height $H^\mathrm{air}=8\ \si{\km}$. Thus~\cite{Levi1980}, the
coefficients for extinction and scattering by air molecules can be
modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4} \exp(-h/H^\mathrm{air})
  \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}
where $\lambda$ is the wavelength, in microns.
\\

\noindent {\bf Inverse transform sampling}: A tool for RT is
Monte-Carlo (MC) simulation. MC considers scattering and extinction as
random phenomena, that are sampled from their probability
distributions.  Sample random numbers that comply with a specified
probability density function can be generated using inverse transform
sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$.

@@

A set of ground-based wide-angle cameras looks upwards
(\cref{fig:groundgrid}), performing {\em integral
  imaging}~\cite{Hong2004} of the sky. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location, capturing raw image
$i_c({\bm{\Theta}})$. This paper reports a first step: formulating a
principle for estimating 3D atmospheric aerosols distributions, using
such data. To theoretically study the feasibility and cross validate
it, we perform RT using two different forward models. A forward model
takes as input a 3D aerosol distribution, and outputs images as if
captured at various viewpoints.  One model uses MC
(Sec.~\ref{sec:monte-carlo-simul}): it is stochastic, slow but
naturally expresses multiple-scattering. Hence, MC rigorously
simulates realistic scenes of arbitrary complexity.
% MC simulations can be made arbitrarily accurate by increasing the
% number of launched %photons. MC methods are highly parallelizable.
The second model uses the single-scattering approximation
(Sec.~\ref{sec:single-scatt-model}). It is less accurate than MC, but
solves RT in an analytic, closed form. This form enables simple
inversion of the model, to estimate the underlying aerosol
distribution (Sec.~\ref{sec:inverse-problem}).

@@

\section{Single-scattering forward model}
\label{sec:single-scatt-model}

As illustrated in Figs.~\ref{fig:groundgrid},\ref{fig:distributions},
The sky is discretized into a grid of $N_{\rm voxels}$ volume elements
(voxels), indexed by $k$, $m$ or $q$.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small Simulated 3D aerosol distributions: {\em Haze blobs}
    [a] and {\em Haze Front}.  Here, an aerosol density unit is
    $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
    area of $50\times 50{\rm km}^2$, extending from the ground up to
    altitude of 10km. The domain is divided into a rectilinear grid
    having $N_{\rm voxels}$ voxels.}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense: inside fog and clouds this model does not
apply. In this model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
Sec.~\ref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in Sec.~\ref{sec:scattering}.

@@

\subsection{Optical depth}
\label{sec:optical-depth}

Denote a SR line segment between the TOA and the center of voxel $k$
by $[{\rm SR},k]$ (See \cref{fig:groundgrid}). This SR intersects
voxel $q$. The intersection line segment has geometric length $l_{\rm
  SR}(q|\Delta z,\Phi^{\rm SR})$, where $\Delta z$ is a voxel's
vertical geometric thickness, and $\Phi^{\rm SR}$ is the Sun
angle. Define a \mbox{$N_{\rm voxels}\times N_{\rm voxels}$} matrix
$\OpDistance^{\mathrm{Sun \rightarrow voxel}}$, whose element $(k,q)$
represents $l_{\rm SR}(q)$:
\begin{equation}
  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  \hspace{-0.05cm}
\end{equation}
Matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is sparse.
Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$ (see
\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
Suppose this LOS intersects voxel $q$. The geometric length of this
intersection line segment is $l_{\rm LOS_c}(m|\Delta z,\Phi^{\rm
  LOS}_c)$.  As in~(\ref{eq:Dsv}), define a $N_{\rm voxels}\times
N_{\rm voxels}$ sparse matrix whose element $(k,m)$ is
\begin{equation}
  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,m) =
  \left\{
    \begin{array}{ll}
      l_{{\rm LOS}_c}(m) & \mbox{ if $m \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}

We focus on situations where, in addition to air molecules, there is a
single type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\DistUnknown}$ is
variable. As a numerical approximation, assume that within any voxel,
the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$
and the aerosol density $n(k)$ are constants, e.g., corresponding to
the value at each voxel center.  Following \cref{eq:tau}, the optical
depth between the TOA and voxel $k$ is
% \begin{equation}
%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
%  \label{eq:lSRn}
%\end{equation}
\begin{equation}
  \tau_{\rm SR}(k)=
  \sum_{q \in[{\rm SR},k]}
  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] l_{\rm SR}(q)
  =\tau_{\rm SR}^{\rm air}(k)+  \sigma^{\rm aerosol}\sum_{q \in[{\rm SR},k]} l_{\rm SR}(q) n(q)
  ,
  \label{eq:lSRn}
\end{equation}
where $\tau_{\rm SR}^{\rm air}(k)=\sum_{q \in[{\rm SR},k]}\beta^{\rm
  air}(q)l_{\rm SR}(q)$.  Let $\vect{\tau}_{\rm SR}$ and
$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
  air}(k)$, respectively. Then, we can write \cref{eq:lSRn} using
matrix notation: \mbox{$\vect{\tau}_{\rm SR}=\vect{\tau}_{\rm SR}^{\rm
    air} + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow
      voxel}} {\DistUnknown}$}.

A similar analysis yields the optical depth along a LOS to voxel $k$,
$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}
Hence, in matrix notation, \cref{eq:tau} yields the total optical
depths corresponding to LOSs (of camera $c$) and SRs that cross all
voxels:
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;.
  \label{eq:tautotal}
\end{equation}

@@

\subsection{Image capture}
\label{sec:captured-image}

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(Eqs.~\ref{eq:beer-lambert},\ref{eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being
oblivious to all the rest.  Overall, light power captured at a pixel
is a weighted sum of the power $p_c(k)$ from all voxels.  This sum is
formulated by a matrix operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
  pix}$ long.  Combining
Eqs.~(\ref{eq:tautotal},\ref{eq:pc},\ref{eq:IcP}), the captured image
is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
  {\bm D}_c{\bm n})] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

\section{Examples}
\label{sec:simul}

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/ref_images.pdf}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the X-Axis of the MC simulation, Single-Scattering
    simulation and a Single-Scattering image created from the
    reconstructed distribution (\cref{sec:optimization-results}).}
  \label{fig:simulation-results1}
\end{figure}
To demonstrate the model, we simulated some scenarios, whose details are as follows.\\
\noindent{\bf Geometry}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$.  Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of $L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm
  B}=255:236:224$.
